Data preparation

### 2023-10-17 paper.Rmd
ordenar codigo

```{r homogeneity,fig.height=3.4,fig.width=6,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '100%'}
# x country   
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3, 
                        homclass=homclass2,
                        # homclass=eindex,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        workst
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# x country
dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))
resits_count <- dfreg %>%
  group_by(country2,country) %>%
  summarise_at(c("redist","homclass",
                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
  as.data.frame()
resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")

@@

```{r mod-homclass,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=dclass3,
                        class5,
                        homclass=homclass2,
                        Q03pcm,
                        # Q03pcm=Q03rm,
                        # Q03pcm=Q03rm,
                        # Q03pcm=zincpc,
                        # Q03rm=
                        # isei08,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        workst,
                        # isolation,  
                        MAINSTAT,
                        # activities,
                        # WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",oecd
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("CHN")) %>%
  # filter(!country2 %in% c("TWN")) %>%
  # filter(!country2 %in% c("ZAF")) %>%
  # filter(!country2 %in% c("FIN")) %>%
  # filter(!country2 %in% c("USA")) %>%
  # filter(!country2 %in% c("GBR")) %>%
  # filter(!country2 %in% c("ISL")) %>%
  # filter(!country2 %in% c("TUR","EST")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
  # filter(PARTLIV %in% c(0,1,2,3)) %>%
  # filter(region %in% c("Northern America","South America")) %>%
  # filter(Q03pcm!="Missing") %>%
    # filter(oecd=="OECD") %>%
  na.omit()

# models <- list(homclass,class,full1,
#                # rob1,rob2,
#                rob4)
cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
coefmap <-  list(homclass ="Class-based network homogeneity",
                 'class3Intermediate class (III+IV)' ='Intermediate Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                  "workstNot in paid work"="Not in labor force",
                 "unionYes" = 'Union membership: Yes',
                 'class3Intermediate class (III+IV):homclass'='Homogeneity x Intermediate Class',
                 'class3Working Class (V+VI+VII):homclass'='Homogeneity x Working Class'
                 )
coefgroup <- list("Social Class (ref: Service Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Homogeneity x Social Class"=9:10
                  )
gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)

models <- list(homclass,class,full1,rob3,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  custom.gof.names = gof1
                )
```

@@

@@

@@

```{r mod-intermacro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
dfreg <- df1 %>% dplyr::select(redist,
                        class3=dclass3,
                        homclass=homclass2,
                        # homclass=eindex,
                        # homclass=ingroup,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        # giniot=gini,
                        giniot=gv_spen,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,
                        union,
                        workst,oecd) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>%
  filter(oecd=="OECD") %>% 
  na.omit()
# T03dim(dfreg)

@@

table(dfreg$gini_disp)

dfreg %>% filter(gini_disp %in%)

>>>>

```{r homogeneity,fig.height=3.4,fig.width=6,fig.cap=c("Class-based network homogeneity by country in the ISSP 2017"), out.width = '100%'}
# x country   
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3, 
                        homclass=homclass,
                        # homclass=eindex,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,country,
                        union,
                        workst
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# x country
dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))
resits_count <- dfreg %>%
  group_by(country2,country) %>%
  summarise_at(c("redist","homclass",
                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
  as.data.frame()
resits_count$country3 <- countrycode::countrycode(sourcevar = resits_count$country,origin = "iso3n",destination = "iso3c")

@@

```{r mod-homclass,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  # filter(!country2 %in% c("CHN")) %>%
  # filter(!country2 %in% c("TWN")) %>%
  # filter(!country2 %in% c("JPN")) %>%
  # filter(!country2 %in% c("ZAF")) %>%
  # filter(!country2 %in% c("PHL")) %>%
  # filter(!country2 %in% c("FIN")) %>%
  # filter(!country2 %in% c("USA")) %>%
  # filter(!country2 %in% c("GBR")) %>%
  # filter(!country2 %in% c("ISL")) %>%
  # filter(!country2 %in% c("TUR","EST")) %>%
  # filter(!country2 %in% c("MEX")) %>%
# filter(!country2 %in% c("HUN")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>% # Paskov & Weisstanner
  # filter(PARTLIV %in% c(0,1,2,3)) %>%
  # filter(!region %in% c("Northern America","South America")) %>%
  # filter(Q03pcm!="Missing") %>%
    # filter(oecd=="OECD") %>%
  na.omit()

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

cap1 <- "Multilevel regression for redistributive preferences, network homogeneity and social class" 
coefmap <-  list(homclass ="Class-based network homogeneity",
                 'class3Intermediate class (III+IV)' ='Intermediate Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                 "workstNot in paid work"="Not in labor force",
                 "unionYes" = 'Union membership: Yes',
                 'homclass:class3Intermediate class (III+IV)'='Homogeneity x Intermediate Class',
                 'homclass:class3Working Class (V+VI+VII)'='Homogeneity x Working Class'
                 )
coefgroup <- list("Social Class (ref: Service Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Homogeneity x Social Class"=9:10
                  )
gofrow <-  list(Controls=c("No","Yes","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA,NA)

models <- list(homclass,full1,rob2,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

m1_df <-
    broom.mixed::tidy(rob1) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
                                                    "class3Working Class (V+VI+VII)",
                                                    "homclass")) 
# %>% mutate(model = "Model 1")
m2_df <-
    broom.mixed::tidy(int_homo) %>% filter(term %in%  c("class3Intermediate class (III+IV)",
                                                        "class3Working Class (V+VI+VII)",
                                                        "homclass",
                                                        "class3Intermediate class (III+IV):homclass",
                                                        "class3Working Class (V+VI+VII):homclass")) %>% mutate(model = "Model 2")

@@

  dwplot(m1_df,
       vline = geom_vline(xintercept = 0,colour = "black",linetype = 1,size=0.01),
       style = "dotwhisker",
       dot_args =  list(size=5),
       whisker_args = list(size=2),
       vars_order = c("homclass",
                      "class3Intermediate class (III+IV)",
          "class3Working Class (V+VI+VII)",
          "class3Intermediate class (III+IV):homclass",
          "class3Working Class (V+VI+VII):homclass")) %>%

     relabel_predictors(
        c("homclass"="Class based network homogeneity",
          "class3Intermediate class (III+IV)"="Intermediate Class (ref: Service class)",
          "class3Working Class (V+VI+VII)"="Working Class",
          "class3Intermediate class (III+IV):homclass"="Homogeneity x Intermediate Class",
          "class3Working Class (V+VI+VII):homclass"="Homogeneity x Working Class"))+
      ggtitle("Multilevel regression for Network segregation, social class and redistributive preferences") +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(
        plot.title = element_text(face = "bold"),
        # legend.position = c(0.007, 0.01),
        # legend.justification = c(0, 0),
        # legend.background = element_rect(colour = "grey80"),
        # legend.title = element_blank(),
        axis.text.y.left = element_text(face = "bold",size = 12)
  )
```

@@

```{r mod-intermacro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjlabelled,haven,stringr,sjPlot)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3=dclass3,
                        homclass=homclass2,
                        # homclass=eindex,
                        # homclass=ingroup,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        # giniot=gini,
                        giniot=gv_spen,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,
                        union,
                        workst,oecd) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>%
  filter(oecd=="OECD") %>% 
  na.omit()
# T03dim(dfreg)

main <- "redist~class3+ homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <-update(base, . ~ . - (1|country2) + (homclass|country2))
anova(giniD_gdp,giniD_rs)
giniD_int<- lmer(formula(paste0(main,"+homclass*gini_disp+logrgdpna","+(homclass|country2)")),data=dfreg)
# summary(giniD_int)

@@

### 2023-10-17 procesamiento/prod_prep.Rmd
ordenar codigo

@@

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE 
                      )
options(scipen=9999) # desactivar notacion cientifica
```

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,GGally,sjlabelled,tidyverse,MLMusingR)
df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
dfTR <- haven::read_dta(here::here("input/data/original/ZA5521_v1-0-0.dta"))
dfES <- haven::read_dta(here::here("input/data/original/ZA5962_v1-0-0.dta"))

# relig <- haven::read_dta(here::here("input/data/original/ZA7570_v2-1-0.dta"))
# religTR <- relig %>% filter(country==792)

df1 <- df1 %>% rename(topbot=TOPBOT)
dfES <- dfES %>% rename(topbot=TOPBOT)
#fix problem with variable names
dfTR <- dfTR %>% rename(SEX=sex,
                        DEGREE=degree,
                        EDUCYRS=educyrs,
                        AGE=age,
                        MAINSTAT=mainstat,
                        UNION=union,
                        WEIGHT=weight,
                        URBRURAL=urbrural,
                        WORK=work,
                        HOMPOP=hompop,
                        EMPREL=emprel,
                        NSUP=nsup,
                        WRKSUP=wrksup,
                        SPEMPREL=spemprel,
                        SPWRKSUP=spwrksup)  
dfES$c_alphan <- NULL
dfTR$c_alphan <- NULL
df2 <- bind_rows(dfES,dfTR)
df1<- bind_rows(df1,df2)
```

@@

sjlabelled::set_label(df1$egal3) <- "Redistributive attitudes (3 items)"
# hist.default(df1$egal3)

df1$egal2<- rowMeans(df1[,c("redist","prefineq")],na.rm = T)
df1$egal2 <- ((df1$egal2-min(df1$egal2,na.rm = T))/(max(df1$egal2,na.rm = T)-min(df1$egal2,na.rm = T)))*100
sjlabelled::set_label(df1$egal2) <- "Redistributive attitudes (2 items)"
# hist.default(df1$egal2)
```

@@

frq(df1$oesch16)
frq(df1$oesch8)

df1 <- df1 %>% 
  mutate(oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))

frq(df1$oesch8)
frq(df1$oesch8spo)
```

@@

# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
df1$eindex<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
sjlabelled::set_label(df1$eindex) <- "EI homophily index"
#frq(df1$eindex)
hist.default(df1$eindex)
df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
hist.default(df1$eindex_gc)

@@

df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
#frq(df1$eindex_s)
hist.default(df1$eindex_s)

df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
hist.default(df1$homclass_s)
```

@@

df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
frq(df1$eindex_w)
hist.default(df1$eindex_w)

df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
hist.default(df1$homclass_s)
```

@@

df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
# frq(df1$eindex)
# hist.default(df1$eindex)

@@

# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
sjlabelled::set_label(df1$eindex2) <- "EI homophily index"
#frq(df1$eindex)
hist.default(df1$eindex2)
df1$eindex2_gc <- group_center(x = df1$eindex2,grp = df1$country)
hist.default(df1$eindex2_gc)

@@

```{r homogeneity-resp-v02}
# EI homophily index
df1$ingroup_res <- NA 
df1 %>% select(ddigclass3res,n_high,n_middle,n_low,ingroup_res)
df1$ingroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
df1$ingroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
df1$ingroup_res <- ifelse(df1$digclass3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
# frq(df1$ingroup_res)

@@

df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
# frq(df1$eindex)
# hist.default(df1$eindex)

df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
df1$homclass_res <- as.numeric(df1$ingroup_res/df1$know_total)
sjlabelled::set_label(df1$homclass_res) <- "Class homogeneity (R's)"
# Weighted EI index
# https://arxiv.org/pdf/2109.00348.pdf
```

@@

# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
df1$eindex3<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
sjlabelled::set_label(df1$eindex3) <- "EI homophily index"
#frq(df1$eindex)
hist.default(df1$eindex)
df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
hist.default(df1$eindex_gc)

@@

```{r}
save(df1,file = here::here("input/data/proc/study1.RData"))
```

>>>>

```{r eval=FALSE, include=FALSE}
knitr::knit(input = here::here("procesamiento/prod_prep.Rmd"));file.remove("prod_prep.md")
```

@@

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE,
                      cache = T
                      )
options(scipen=9999) # desactivar notacion cientifica
```

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,GGally,sjlabelled,tidyverse,MLMusingR)
df1 <- haven::read_dta(here::here("input/data/original/ZA6980_v2-0-0.dta"))
dfTR <- haven::read_dta(here::here("input/data/original/ZA5521_v1-0-0.dta"))
dfES <- haven::read_dta(here::here("input/data/original/ZA5962_v1-0-0.dta"))
dfTR$weight <- 1
df1 <- df1 %>% rename(topbot=TOPBOT)
dfES <- dfES %>% rename(topbot=TOPBOT)
# fix problem with variable names
dfTR <- dfTR %>% rename(SEX=sex,
                        DEGREE=degree,
                        EDUCYRS=educyrs,
                        AGE=age,
                        MAINSTAT=mainstat,
                        UNION=union,
                        WEIGHT=weight,
                        URBRURAL=urbrural,
                        WORK=work,
                        HOMPOP=hompop,
                        EMPREL=emprel,
                        NSUP=nsup,
                        WRKSUP=wrksup,
                        SPEMPREL=spemprel,
                        SPWRKSUP=spwrksup)

dfES$c_alphan <- NULL
dfTR$c_alphan <- NULL
df2 <- bind_rows(dfES,dfTR)
df1<- bind_rows(df1,df2)
```

@@

sjlabelled::set_label(df1$egal3) <- "Redistributive attitudes (3 items)"
# #hist.default(df1$egal3)

df1$egal2<- rowMeans(df1[,c("redist","prefineq")],na.rm = T)
df1$egal2 <- ((df1$egal2-min(df1$egal2,na.rm = T))/(max(df1$egal2,na.rm = T)-min(df1$egal2,na.rm = T)))*100
sjlabelled::set_label(df1$egal2) <- "Redistributive attitudes (2 items)"
# #hist.default(df1$egal2)
```

@@

df1 <- df1 %>% 
  mutate(oesch16spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))

frq(df1$oesch16)

df1$oesch16 <- as_labelled(df1$oesch16)
df1$oesch16spo <- as_labelled(df1$oesch16spo)
# # Upper-middle class
#  [1] "'Large employers'"
#  [2] "'Self-employed professionals'"
# 
#  [9] "'Higher-grade managers and administrators'"
# [10] "'Lower-grade managers and administrators'"

#  [5] "'Technical experts'"
#  [6] "'Technicians'"
# 
# [13] "'Socio-cultural professionals'"
# [14] "'Socio-cultural semi-professionals'"

# # Lower-middle class
#  [3] "'Small business owners with employees'"
#  [4] "'Small business owners without employees'"
# [11] "'Skilled clerks'"
# 
# # Working class
#  [7] "'Skilled manual'"
#  [8] "'Low-skilled manual'"
# 
# [12] "'Unskilled clerks'"
# [15] "'Skilled service'"
# [16] "'Low-skilled service'"

df1$oesch3res <- car::recode(df1$oesch16,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
df1$oesch3spo <- car::recode(df1$oesch16spo,recode="c(1,2,9,10,5,6,13,14)=1;c(3,4,11)=2;c(7,8,12,15,16)=3")
```

@@

# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
df1$eindex<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
sjlabelled::set_label(df1$eindex) <- "EI homophily index"
#frq(df1$eindex)
#hist.default(df1$eindex)
df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
#hist.default(df1$eindex_gc)

@@

df1$eindex_s<- (df1$ingroup_s-df1$outgroup_s)/(df1$outgroup_s+df1$ingroup_s)
sjlabelled::set_label(df1$eindex_s) <- "EI homophily index (strong ties)"
#frq(df1$eindex_s)
#hist.default(df1$eindex_s)

df1 %>% select(class3,n_high_s,n_middle_s,n_low_s,outgroup_s,ingroup_s,eindex_s)
df1$homclass_s <- as.numeric(df1$ingroup_s/df1$know_total_s)
sjlabelled::set_label(df1$homclass_s) <- "Class homogeneity (strong ties)"
#hist.default(df1$homclass_s)
```

@@

df1$eindex_w<- (df1$ingroup_w-df1$outgroup_w)/(df1$outgroup_w+df1$ingroup_w)
sjlabelled::set_label(df1$eindex_w) <- "EI homophily index (weak ties)"
frq(df1$eindex_w)
#hist.default(df1$eindex_w)

df1 %>% select(class3,n_high_w,n_middle_w,n_low_w,outgroup_w,ingroup_w,eindex_w)
df1$homclass_w <- as.numeric(df1$ingroup_w/df1$know_total_w)
sjlabelled::set_label(df1$homclass_w) <- "Class homogeneity (weak ties)"
#hist.default(df1$homclass_s)
```

@@

df1$eindex_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
# frq(df1$eindex)
# #hist.default(df1$eindex)

@@

# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
df1$eindex2<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
sjlabelled::set_label(df1$eindex2) <- "EI homophily index"
#frq(df1$eindex)
#hist.default(df1$eindex2)
df1$eindex2_gc <- group_center(x = df1$eindex2,grp = df1$country)
#hist.default(df1$eindex2_gc)

@@

```{r homogeneity-resp-v02}
# EI homophily index
df1$ingroup_res <- NA 
df1 %>% select(digclass3res,n_high,n_middle,n_low,ingroup_res)
df1$ingroup_res <- ifelse(df1$digclass3res=="Service Class (I+II)",df1$n_high,df1$ingroup_res)
df1$ingroup_res <- ifelse(df1$digclass3res=="Intermediate class (III+IV)",df1$n_middle,df1$ingroup_res)
df1$ingroup_res <- ifelse(df1$digclass3res=="Working Class (V+VI+VII)",df1$n_low,df1$ingroup_res)
# frq(df1$ingroup_res)

@@

df1$eindex2_res<- (df1$ingroup_res-df1$outgroup_res)/(df1$outgroup_res+df1$ingroup_res)
sjlabelled::set_label(df1$eindex_res) <- "EI homophily index (R's)"
# frq(df1$eindex)
# #hist.default(df1$eindex)

df1 %>% select(digclass3res,n_high,n_middle,n_low,outgroup_res,ingroup_res,eindex_res)
df1$homclass2_res <- as.numeric(df1$ingroup_res/df1$know_total)
sjlabelled::set_label(df1$homclass2_res) <- "Class homogeneity (R's)"
# Weighted EI index
# https://arxiv.org/pdf/2109.00348.pdf
```

@@

# df1$eindex<- (df1$outgroup-df1$ingroup)/(df1$outgroup+df1$ingroup)
df1$eindex3<- (df1$ingroup-df1$outgroup)/(df1$outgroup+df1$ingroup)
sjlabelled::set_label(df1$eindex3) <- "EI homophily index"
#frq(df1$eindex)
#hist.default(df1$eindex)
df1$eindex_gc <- group_center(x = df1$eindex,grp = df1$country)
#hist.default(df1$eindex_gc)

@@

```{r}
save(df1,file = here::here("input/data/proc/study1.RData"))
knitr::knit(input = here::here("procesamiento/prod_prep-macro.Rmd"));file.remove("prod_prep-macro.md")
```
